---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pathologie

> Tidy ICD-10-CM Interface

<!-- badges: start -->
<!-- badges: end -->

## :package: Installation

You can install **pathologie** from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("andrewallenbruce/pathologie")
```

## :beginner: Usage

```{r setup, message=FALSE, warning=FALSE}
library(pathologie)
library(dplyr)
```


```{r}
icd10cm(icd = c("I10", "I15.0")) |> 
  glimpse()
```


```{r}
icd10api(icd_code = "I1")
```



------------------------------------------------------------------------------

## :balance_scale: Code of Conduct

Please note that the **`pathologie`** project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/pathologie/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## :classical_building: Governance

This project is primarily maintained by [Andrew Bruce](https://github.com/andrewallenbruce). Other authors may occasionally assist with some of these duties.
