---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pathologie

> Tidy ICD-10-CM Interface

<!-- badges: start -->
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/pathologie/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/pathologie)
[![Code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/pathologie.svg)](https://github.com/andrewallenbruce/pathologie)
[![Last commit](https://img.shields.io/github/last-commit/andrewallenbruce/pathologie.svg)](https://github.com/andrewallenbruce/pathologie/commits/main)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/pathologie/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/pathologie)
<!-- badges: end -->

## :package: Installation

You can install **pathologie** from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("andrewallenbruce/pathologie")
```

## :beginner: Usage

```{r setup, message=FALSE, warning=FALSE}
library(pathologie)
library(fuimus)
library(dplyr)
```


```{r}
icd10cm(icd = c("I10", "I15.0")) |> 
  glimpse()
```


```{r}
icd10api(icd_code = "I1")
```

# ICD-10-CM Conflict Rules

```{r}
ex_data() |>
  dplyr::mutate(
    patient_age = years_floor(
      date_of_birth, 
      date_of_service
      )
    ) |>
  dplyr::left_join(
    search_edits(), 
    by = dplyr::join_by(icd_code), 
    relationship = "many-to-many"
    ) |>
  dplyr::filter(
    icd_conflict_group == "Age"
    ) |>
  dplyr::mutate(
    conflict = apply_age_edits(
      rule = icd_conflict_rule,
      age = patient_age
      )
    )
```


------------------------------------------------------------------------------

## :balance_scale: Code of Conduct

Please note that the **`pathologie`** project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/pathologie/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## :classical_building: Governance

This project is primarily maintained by [Andrew Bruce](https://github.com/andrewallenbruce). Other authors may occasionally assist with some of these duties.
