---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pathologie

> Tidy ICD-10-CM Interface

<!-- badges: start -->
![GitHub R package version](https://img.shields.io/github/r-package/v/andrewallenbruce/pathologie?style=flat-square&logo=R&label=Package&color=%23192a38)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/pathologie/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/pathologie)
[![Code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/pathologie.svg)](https://github.com/andrewallenbruce/pathologie)
[![Last commit](https://img.shields.io/github/last-commit/andrewallenbruce/pathologie.svg)](https://github.com/andrewallenbruce/pathologie/commits/main)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/pathologie/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/pathologie)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
<!-- badges: end -->

## :package: Installation

You can install **pathologie** from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("andrewallenbruce/pathologie")
```

## :beginner: Usage

```{r setup, message=FALSE, warning=FALSE}
library(pathologie)
library(dplyr)
```


```{r}
icd10cm(icd = c("I15.0")) |> glimpse()
```

## NLM ICD-10-CM API

```{r}
icd10api(icd_code = "I1")
```

## Conflict Edit Rules

```{r}
ex_data() |>
  reframe(dob = date_of_birth,
          dos = date_of_service,
          icd_code,
          age = years_floor(dob, dos)) |>
  right_join(search_edits(group = "Age"), 
             by = join_by(icd_code)) |>
  mutate(
    conflict = apply_age_edits(icd_conflict_rule, age),
    dob = NULL,
    dos = NULL,
    icd_conflict_group = NULL
  )
```


------------------------------------------------------------------------------

## :balance_scale: Code of Conduct

Please note that the **`pathologie`** project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/pathologie/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## :classical_building: Governance

This project is primarily maintained by [Andrew Bruce](https://github.com/andrewallenbruce). Other authors may occasionally assist with some of these duties.
