---
title: "pathologie"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pathologie}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
  )

library(dplyr)
library(gt)
library(pathologie)
```

```{r}
library(pathologie)
```


# ICD-10-CM

```{r}
icd10cm(icd = "T76.02XA") |> 
  mutate(Chapter = paste0("* ", icd_ch_name, " \n ", "* Range: [", icd_ch_range, "]"),
         Section = paste0("* ", icd_sec_name, " \n ", "* Range: [", icd_sec_range, "]")
         ) |>
  select("ICD-10-Code"   = icd_code, 
         Description     = icd_description, 
         Chapter,
         Section,
         Abbreviation    = icd_ch_abb,
         "Conflict Group" = icd_conflict_group,
         "Conflict Rule"  = icd_conflict_rule) |> 
  display_long() |>
  gt(groupname_col       = "name", 
     row_group_as_column = TRUE) |>
  fmt_markdown() |> 
  gt_style(tablign       = "right", 
           tabsize       = 16, 
           tabwt         = "bold") |> 
  tab_style(
      style              = cell_text(
      font               = google_font(name = "Fira Code")),
      locations          = cells_body(
        columns          = contains("value"))) |>
  tab_style(
    style                = list(
      cell_fill(color    = "powderblue"),
      cell_text(weight   = "bold"),
      cell_borders(
      sides              = c("all"),
      color              = "powderblue",
      weight             = px(3))
      ),
    locations            = cells_row_groups())
```


# The NLM's ICD-10-CM API

The [National Library of Medicine](https://clinicaltables.nlm.nih.gov/apidoc/icd10cm/v3/doc.html)'s ICD-10-CM API is a RESTful API that provides access to the current ICD-10-CM code set. 

The API allows users to search for codes by code or keyword(term), and returns the code and its description. Searching is case insensitive and greedy The following are some examples:


> Returns the seven ICD-10 codes beginning with `A15`:

```{r}
icd10api(code = "A15")
```

> Returns all 344 ICD-10 codes associated with tuberculosis:

```{r}
icd10api(term = "tuber")
```

> Returns the two ICD-10 codes associated with pleurisy:

```{r}
icd10api(term = "pleurisy")
```

## The `field` Parameter

The `field` parameter allows users to specify whether they want to search for ICD-10-CM codes by the codes themselves or by terms associated with their description. It defaults to `"code"` and it's behavior warrants some explanation.

If you're searching for codes beginning with a certain letter, you must set the `field` parameter to `"code"` or it will return both codes and terms that contain that letter. 


For instance, the following call returns ICD-10 **codes** and **descriptions** containing the letter "Z":


```{r}
icd10api(code = "z", limit = 50)
```


While the call below returns only the ICD-10 **codes** containing "Z":


```{r}
icd10api(code = "z", field = "code", limit = 50)
```

